Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 conclusion.tex
fixing BW head-2-head comparision.

Thanks to the efforts captured in this paper, the time-averaged utilization of
Titan has consistently been upwards of 90\%. Compare this to the time averaged
utilization of other similar leadership machines such as NSF's flagship Blue
Waters, where the average utilization fluctuates between 60-80\% (XDMoD)
machine~\cite{bw-sucks}. These
% impressive if not
unprecedented efficiency gains aside, this work is just a starting point towards
more effective operational models for future leadership and online analytical
platforms~\cite{foap-url}. These platforms will have to support ever increasing
complex workloads with varying models for dynamic resource federation. Recent
efforts with Google Cloud for the CMS experiment --
HEPCloud~\cite{hepcloud,googlehep} represent similar yet different approaches
to dynamic resource federation.

>>>>

The 52M core hours used by ATLAS, via PanDA, is over 2\% of the total
utilization on Titan over the same period, bringing the time-averaged
utilization of Titan to be consistently upwards of 90\%. Given that the
average average utilization of most other leadership class machines is less
(e.g., NSF's flagship Blue Waters the average utilization fluctuates between
60-80\% (see XDMoD\cite{bw-sucks})) there is ample headroom for similar
approaches elsewhere. These unprecedented efficiency gains aside, this work is
just a starting point towards more effective operational models for future
leadership and online analytical platforms~\cite{foap-url}. These platforms
will have to support ever increasing complex workloads with varying models for
dynamic resource federation. Recent efforts with Google Cloud for the CMS
experiment -- HEPCloud~\cite{hepcloud,googlehep} represent similar yet
different approaches to dynamic resource federation.
